New and old ways to chase a rabbit:\\ Differential item functioning detection methods

### 2020-03-04 paper/paper_2b_anchor_points.Rmd
use git search

tmp <- 
    multipleGroup(
        data,
        1,
        itemtype = "Rasch",
        groups,
        invariance = c("free_var"),
        pars = "values"
    ) %>% 
    as_tibble()

tmp$value[length(tmp$value) - 1] <- gini_results$gini_anchor_points

mod <- 
    multipleGroup(
        data,
        1,
        itemtype = "Rasch",
        groups,
        pars = tmp %>% as.data.frame(),
        SE = TRUE,
        technical = list(NCYCLES = 500),
        verbose = FALSE,
    )

>>>>

mod <- gini_results_to_final_mod(gini_results$gini_anchor_points, data, groups)
